Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-23 article/article.tex
Commit 2024-06-23 18:14

The magnitude of the ECE events does not exceeds the values reported for
sites with more favourable conditions for the phenomenon. The
climatological characteristic of the ECE events, showed that the most
active months are spread on half of the year (March -- June and
September and October). We found that CE conditions, can have a duration
of more than an hour in rare cases, with the bulk of the cases having a
duration under 5 minutes. Some of the characteristics of CE and ECE
events we analysed, have strong similarities with results by
\citet{Vamvakas2020}, for a city southern of Thessaloniki, with the
analogues differences on the intensity of the solar radiation.

An interpretation of the CE trends, shows that the interaction of GHI
with the clouds, through this 30 year period, is a dynamic phenomenon
that's needs further investigation. Although, to approach it, we need
more long-term observations of AOD and clouds characteristics.

>>>>

The magnitude of the ECE events does not exceed the values reported for
sites with more favourable conditions for the phenomenon. The
climatological characteristic of the ECE events, showed that the most
active months are spread in half of the year (March -- June, September
and October). We found that CE conditions, can have a duration of more
than an hour in rare cases, with the bulk of the cases having a duration
under 5 minutes. Some of the characteristics of CE and ECE events we
analysed have strong similarities with results by \citet{Vamvakas2020}
for the city of Patras, south of Thessaloniki, with analog differences
on the intensity of the solar radiation.

An interpretation of the CE trends shows that the interaction of GHI
with the clouds, through this 30 year period, is a dynamic phenomenon
that needs further investigation. Although, to approach it, we need more
long-term observations of AOD and clouds characteristics.
